### 2015-08-08 ThesisJo/derivations.tex
la2pdf commit - 2015:08:08	23:04:38	(Sat 8.Aug)

\begin{align}
\text{Equivalent Noise Bandwidth} &= \frac{\text{Noise Power}}{\text{Coherent Power Gain}} = \frac{N_0\sumb{m}{}w_m^2}{\big|\sumb{m}{}w_m\big|^2}
\end{align}

@@

\begin{align}
\text{Scallopping loss} &= \frac{\left|W\left(\frac{\pi}{2OMd}\right)\right|}{W(0)} = \frac{\left|\sumb{m}{}w_m\;e^{-j\k\cdot\p_m}\right|}{\sumb{m}{}w_m}
\end{align}

Worst Case Processing Loss = Prosessing Loss + Scallopping Loss

>>>>

\begin{align}
\text{Equivalent Noise Bandwidth} &= \frac{\text{Noise Power}}{\text{Coherent Power Gain}} = \frac{\frac{N_0}{{\color{red}d}}\sumb{m}{}w_m^2}{\big|\sumb{m}{}w_m\big|^2}
\end{align}

@@

\begin{align}
\text{Scallopping loss} &= \frac{\left|W\left(\frac{\pi}{2{\color{red}O}Md}\right)\right|}{W(0)} = \frac{\left|\sumb{m}{}w_m\;e^{-j\k\cdot\p_m}\right|}{\sumb{m}{}w_m}
\end{align}

\begin{align}
\text{Scallopping loss} &= \text{Prosessing Loss}_\text{dB} + \text{Scallopping Loss}_\text{dB} 
= 
\end{align}
Worst Case Processing Loss = Prosessing Loss + Scallopping Loss
